### 2016-07-11 capability-machine.tex
simplified semantics

  \sem{\jmp{\lv}}(\Phi)                    & = 
                                                 \text{if }\memreg(lv) = c \\
                                                 \quad\text{and }c=(\perm,\start,\addrend,\addr)\\
                                                 \quad\text{and }\executeAllowed{\perm}

@@

                                                 \text{if $\nonZero{\memreg(\rv)}$} \\ 
                                                 \quad\text{and $\memreg(lv) = c$} \\
                                                 \quad\text{and $c=(\perm,\start,\addrend,\addr)$}\\
                                                 \quad\text{and $\executeAllowed{\perm}$}
                                               \\ %TODO Maybe combine with jump. (failed + this)

@@

                                                 \text{if } r_1 \neq \pcreg \\
                                                 \quad\text{and }\memreg(r_2) = (\perm,\start,\addrend,\addr) = \var{c} \\

@@

                                                 \stdUpdatePc{\updateReg{r_1}{\memreg(\rv)}} & \text{if $r_1 \neq \pcreg$} \\ % For now we do this, so you need to use a jump to move stuff into pc.

@@

@@

\\ % In the M-Machine, lea checks whether the pointer stay within the allowed range in the pointer.

@@

                                                   \text{if $r_1 \neq \pcreg$}\\
                                                   \quad\text{and $\memreg(\rv_1) = c'$}\\

@@

                                                              \text{if $r_1 \neq \pcreg$}\\
                                                              \quad\text{and for $i \in \{1,2\}$}\\
                                                              \qquad\text{$n_i = \rv_i$ or $n_i = \memreg{\rv_i}$}\\
                                                              \qquad\text{and in either case $n_i \in \ints$}

>>>>

  \sem{\jmp{\lv}}(\Phi)                    & = \updateReg{\pcreg}{\updatePcPerm{\var{c}}} \\

@@

                                                 \text{if $\nonZero{\memreg(\rv)}$} 

@@

                                                 \text{if }\memreg(r_2) = (\perm,\start,\addrend,\addr) = \var{c} \\

@@

                                                 \stdUpdatePc{\updateReg{r_1}{\memreg(\rv)}} & \\ % For now we do this, so you need to use a jump to move stuff into pc.

@@

\\

@@

\\
 % In the M-Machine, lea checks whether the pointer stay within the allowed range in the pointer.

@@

                                                   \text{if $\memreg(\rv_1) = c'$}\\

@@

                                                              \text{if for $i \in \{1,2\}$}\\
                                                              \quad\text{$n_i = \rv_i$ or $n_i = \memreg{\rv_i}$}\\
                                                              \quad\text{and in either case $n_i \in \ints$}
